Master's Project Journal

### 2019-03-19 conf_paper/paper.tex
page 1 done

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[british]{babel}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{System Architecture}

>>>>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{float}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[british]{babel}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{System Architecture}
An ADPLL network as the name would suggest is created from a number of ADPLLs that coupled using digital phase comparators which attempt to measure the phase error between two oscillators, with each non edge node being connected to four neighbours. Figure \ref{fig:adpll_network} illustrates such a system on a small scale. The individual ADPLLs are made up of a digitally controllable oscillator, an error combination block and a digital loop filter with the aforementioned digital phase detectors lying between each pair of oscillators.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.25\textwidth]{example}
	\caption{ADPLL Architecture.}
	\label{fig:adpll_network}
	\includegraphics[width=0.25\textwidth]{example}
	\caption{ADPLL Architecture.}
	\label{fig:adpll_base}
\end{figure}
 Figure \ref{fig:adpll_base} demonstrates the ADPLL design used in this paper.
